---
title: "Visualization of a data analysis pipeline"
subtitle: 'From data cleaning to model interpretation'
author: "<br><br>Yikai Zhao&nbsp;&nbsp;&nbsp;`r anicon::faa('twitter', animate='float', rtext='&nbsp;@zhao_yikai')`"
institute: "Looking for a full time position as Data scientist"
date: "25-Oct-2018 &nbsp;&nbsp; `r anicon::faa('link', animate='vertical', rtext='&nbsp;ykzhao.com', color='white')`"
output:
  xaringan::moon_reader:
    
    lib_dir: libs
    css: ["assets/shinobi.css", "ninjutsu", "assets/ninpo.css"]
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan

### /ʃaː.'riŋ.ɡan/

---
class: inverse, center, middle

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio ]
