



class: split-50

.column.bg-main1[.content.vmiddle[

# To achieve great .orange[predicability] and .orange[explanabiity]
# XGBoost model is used
# A Bayesian hyperparameter tuning was conducted to find the optimal combination of hyperparamters from our XGBoost model


]]

.column.bg-main5[.content.vmiddle.center[


```{r, echo = F, warning= F, message=F}
train1 = readRDS("data/training_x.rds")
train_y_include = readRDS("data/training_y_included.rds")
library(xgboost)
label_train <- train_y_include["SalePrice"]

# put our testing & training data into two seperates Dmatrixs objects
dtrain <- xgb.DMatrix(data = as.matrix(train1), label= as.matrix(label_train))
#dtest <- xgb.DMatrix(data = as.matrix(test1))

default_param <-list(
        objective = "reg:linear",
        booster = "gbtree",
        eta= 0.114, #default = 0.3
        gamma=0.009,
        max_depth=3, #default=6
        min_child_weight=4, #default=1
        subsample=0.975,
        colsample_bytree=0.503,
        colsample_bylevel = 0.564,
        lambda = 2.631,
        alpha = 0.004
)

xgb_mod <- xgb.train(data = dtrain, params=default_param, nrounds = 178)

library(Ckmeans.1d.dp) #required for ggplot clustering
mat <- xgb.importance (feature_names = colnames(train1),model = xgb_mod)
xgb.ggplot.importance(importance_matrix = mat[1:20], rel_to_first = TRUE)+
  yikai_labels+
  theme_bw()
  yikai_themes+
  labs("Feature importance through XGBoost")

```



]]



---


class: split-50

.column.bg-main1[.content.vmiddle[

# We could also visualize the SHAP value  between variables


]]



.column.bg-main5[.content.vmiddle.center[


```{r, echo = F, warning= F, message=F}
train1 = readRDS("data/training_x.rds")
train_y_include = readRDS("data/training_y_included.rds")
library(xgboost)
label_train <- train_y_include["SalePrice"]

  


```

```{r,warning=F, message = F}
library('SHAPforxgboost')

mod <- xgboost::xgboost(data = as.matrix(train1), label = as.matrix(train_df$SalePrice), 
                       xgb_param = default_param, nrounds = 301,
                       verbose = FALSE, nthread = parallel::detectCores() - 2,
                       early_stopping_rounds = 8)
shap_values <- shap.values(xgb_model = mod, X_train = train1)

shap_long <- shap.prep(xgb_model = mod, X_train = train1)

top20_names = shap_long %>%
  select(variable, mean_value) %>%
  arrange(desc(mean_value)) %>%
  unique() %>%
  top_n(20)

top20_names$variable = droplevels(top20_names$variable)
top_20_feature_field = 
  train1 %>%
  select(as.character(top20_names$variable))

mod_20 <- xgboost::xgboost(data = as.matrix(top_20_feature_field), label = as.matrix(train_df$SalePrice), 
                       xgb_param = default_param, nrounds = 301,
                       verbose = FALSE, nthread = parallel::detectCores() -2,
                       early_stopping_rounds = 8)
shap_long_20 <- shap.prep(xgb_model = mod_20, X_train = as.matrix(top_20_feature_field))



shap.plot.dependence(data_long = shap_long, x = 'TotalSqFeet', y = 'TotalSqFeet', color_feature = 'OverallQual') + 
  ggtitle("(A) SHAP values of TotalSqFeet vs. TotalSqFeet")+
  xlim(c(-4, 3)) +
  labs(title = "SHAP values of TotalSqFeet colored by OverallQual")+
  yikai_labels+
  yikai_themes+
  theme(axis.ticks = element_blank())+
  theme(panel.grid.major.y = element_blank())+
  theme(legend.direction = "horizontal")+
  theme(legend.position = c(0.3, 0.7))+
  theme(legend.text = element_text(size = 6))+
  theme(legend.title = element_text(size = 6))

  
grid::grid.raster(logo, x = 0.79, y = 0.91, just = c('left', 'bottom'), width = unit(1.5, 'inches'))
```



]]



---

class split-50

.column.bg-main1[.content.vmiddle[

# We could also visualize the interactions between variables via SHAP values


]]


.column.bg-main1[.content.vmiddle[


```{r}
shap_int = read_rds("data/shap_interaction_plot_data.rds")
shap.plot.dependence(data_long = shap_long_20,
                           data_int = shap_int,
                           x= "TotalSqFeet", y = "OverallQual", 
                           color_feature = "OverallQual")
```



]]




---




```{r forceplot, warning =F, echo = F}
# force plot
plot_data <- shap.prep.stack.data(shap_contrib = shap_values$shap_score, top_n = 10, n_groups = 6)

shap.plot.force_plot(plot_data, zoom_in_location = 500, y_parent_limit = c(-1.5,1.5))


```










