



class: split-50

.column.bg-main1[.content.vmiddle[

# XGBoost model was used to achieve great .orange[predicability] and .orange[explanability], 
Used bayesian hyperparameter tuning to find the optimal combination of hyperparamters of the XGBoost model


]]

.column.bg-main5[.content.vmiddle.center[


```{r, echo = F, warning= F, message=F, out.width= "90%"}

train1 = readRDS("data/training_x.rds")
train_y_include = readRDS("data/training_y_included.rds")
library(xgboost)
label_train <- train_y_include["SalePrice"]

# put our testing & training data into two seperates Dmatrixs objects
dtrain <- xgb.DMatrix(data = as.matrix(train1), label= as.matrix(label_train))
#dtest <- xgb.DMatrix(data = as.matrix(test1))

default_param <-list(
        objective = "reg:linear",
        booster = "gbtree",
        eta= 0.114, #default = 0.3
        gamma=0.009,
        max_depth=3, #default=6
        min_child_weight=4, #default=1
        subsample=0.975,
        colsample_bytree=0.503,
        colsample_bylevel = 0.564,
        lambda = 2.631,
        alpha = 0.004
)

xgb_mod <- xgb.train(data = dtrain, params=default_param, nrounds = 178)

library(Ckmeans.1d.dp) #required for ggplot clustering
mat <- xgb.importance (feature_names = colnames(train1),model = xgb_mod)
xgb.ggplot.importance(importance_matrix = mat[1:20], rel_to_first = TRUE, n_clusters = 2)+
 yikai_labels+
 theme_bw()+
 theme(panel.grid.major = element_blank())+
 yikai_themes +
 scale_fill_manual(values = c( "#f9b282", "#de6b35"))+
  theme(legend.position = "none")+
  theme(text= element_text(color = "grey40"))+
  theme(axis.text = element_text(color = "grey40"))+
  theme(axis.ticks = element_blank())
    

grid::grid.raster(logo, x = 0.79, y = 0.91, just = c('left', 'bottom'), width = unit(1.5, 'inches'))
    
```



]]



---


class: split-50

.column.bg-main1[.content.vmiddle[

# We could visualize the global importance of features <sup>1</sup>
<br>
<br>
<br>
<br>
<br>
<br>


.footnote[

[1]  This powerpoint is to show the visualizations, not to interpret the results. For more details, please refer [here](https://github.com/slundberg/shap)

]

]]



.column.bg-main5[.content.vmiddle.center[


```{r, echo = F, warning= F, message=F}
train1 = readRDS("data/training_x.rds")
train_y_include = readRDS("data/training_y_included.rds")
library(xgboost)
label_train <- train_y_include["SalePrice"]

  


```

```{r,warning=F, message = F, echo = F, out.width= "90%"}
library('SHAPforxgboost')
train_df = readRDS("data/training_y_included.rds")

mod <- xgboost::xgboost(data = as.matrix(train1), label = as.matrix(train_df$SalePrice), 
                       xgb_param = default_param, nrounds = 301,
                       verbose = FALSE, nthread = parallel::detectCores() - 2,
                       early_stopping_rounds = 8)
shap_values <- shap.values(xgb_model = mod, X_train = train1)

shap_long <- shap.prep(xgb_model = mod, X_train = train1)

top20_names = shap_long %>%
  select(variable, mean_value) %>%
  arrange(desc(mean_value)) %>%
  unique() %>%
  top_n(20)

top20_names$variable = droplevels(top20_names$variable)
top_20_feature_field = 
  train1 %>%
  select(as.character(top20_names$variable))

mod_20 <- xgboost::xgboost(data = as.matrix(top_20_feature_field), label = as.matrix(train_df$SalePrice), 
                       xgb_param = default_param, nrounds = 301,
                       verbose = FALSE, nthread = parallel::detectCores() -2,
                       early_stopping_rounds = 8)
shap_long_20 <- shap.prep(xgb_model = mod_20, X_train = as.matrix(top_20_feature_field))



shap_top20 = shap_long %>%
  filter(variable %in% top20_names$variable)
shap_top20$variable = droplevels(shap_top20$variable)

shap.plot.summary(shap_top20) + yikai_labels + yikai_themes + 
  ggtitle("Global feature importance in SHAP")+
  labs(title = "SHAP values of TotalSqFeet")+
  yikai_labels+
  yikai_themes+
  theme(axis.ticks = element_blank())+
  theme(panel.grid.major.y = element_blank())+
  theme(legend.direction = "horizontal")+
  theme(legend.position = "bottom")+
  theme(legend.text = element_text(size = 6))+
  theme(legend.title = element_text(size = 6))

  
grid::grid.raster(logo, x = 0.79, y = 0.91, just = c('left', 'bottom'), width = unit(1.5, 'inches'))
```



]]




---


class: split-50

.column.bg-main1[.content.vmiddle[

# We could also visualize the .purple[SHAP] values of an individual variable



]]



.column.bg-main5[.content.vmiddle.center[


```{r, echo = F, warning= F, message=F}
train1 = readRDS("data/training_x.rds")
train_y_include = readRDS("data/training_y_included.rds")
library(xgboost)
label_train <- train_y_include["SalePrice"]

  


```

```{r,warning=F, message = F, echo = F, out.width= "90%"}
library('SHAPforxgboost')
train_df = readRDS("data/training_y_included.rds")

mod <- xgboost::xgboost(data = as.matrix(train1), label = as.matrix(train_df$SalePrice), 
                       xgb_param = default_param, nrounds = 301,
                       verbose = FALSE, nthread = parallel::detectCores() - 2,
                       early_stopping_rounds = 8)
shap_values <- shap.values(xgb_model = mod, X_train = train1)

shap_long <- shap.prep(xgb_model = mod, X_train = train1)

top20_names = shap_long %>%
  select(variable, mean_value) %>%
  arrange(desc(mean_value)) %>%
  unique() %>%
  top_n(20)

top20_names$variable = droplevels(top20_names$variable)
top_20_feature_field = 
  train1 %>%
  select(as.character(top20_names$variable))

mod_20 <- xgboost::xgboost(data = as.matrix(top_20_feature_field), label = as.matrix(train_df$SalePrice), 
                       xgb_param = default_param, nrounds = 301,
                       verbose = FALSE, nthread = parallel::detectCores() -2,
                       early_stopping_rounds = 8)
shap_long_20 <- shap.prep(xgb_model = mod_20, X_train = as.matrix(top_20_feature_field))



shap.plot.dependence(data_long = shap_long, x = 'TotalSqFeet', y = 'TotalSqFeet', color_feature = 'TotalSqFeet') + 
  ggtitle("(A) SHAP values of TotalSqFeet vs. TotalSqFeet")+
 xlim(c(-4, 3)) +
  labs(title = "SHAP values of TotalSqFeet")+
  yikai_labels+
  yikai_themes+
  theme(axis.ticks = element_blank())+
  theme(panel.grid.major.y = element_blank())+
  theme(legend.direction = "horizontal")+
  theme(legend.position = c(0.3, 0.7))+
  theme(legend.text = element_text(size = 6))+
  theme(legend.title = element_text(size = 6))

  
grid::grid.raster(logo, x = 0.79, y = 0.91, just = c('left', 'bottom'), width = unit(1.5, 'inches'))
```



]]








